### 2012-02-13 exam3/1.tex
Small tweaks from taking exam.

(define-class a% (fields cookoo))
(define-class b% (fields gaga bang))
(define-class c% (fields doodle))
\end{verbatim}

@@

\item \verb|replace-gaga| - produces a \verb|P| like this one, but
  with any \verb|gaga| field replaced by the given string.

\item \verb|same-gaga-cookoo?| - produces true for any \verb|P| which
  contains a \verb|B| whose \verb|gaga| is equal to a given string and
  whose \verb|bang| is an \verb|A| whose \verb|cookoo| is equal to
  another given string.  Produces false otherwise.

@@

\begin{solution}
\begin{verbatim}
;;> [6 pts -- contract and purpose for each method]
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-gaga : String -> P
;;   Replace gaga field (if any) of this P with given string.
;; - same-gaga-cookoo? : String String -> Boolean
;;   Is there a B within this P with given gaga field and cookoo field?

;;> [0 pts -- not required, but write something]
;; An A implements:
;; - cookoo : -> String
;;   Get the cookoo string.

;;> [2 pts] In a%: 
(define (size) 5)
(define (replace-gaga str) this)
(define (same-gaga-cookoo? g c) false)

;;> [3 pts] In b%:
(define (size) 8)
(define (replace-gaga str)
  (new b% str (this . bang)))
(define (same-gaga-cookoo? g c)
  (and (string=? g (this . gaga))
       (string=? c (this . bang . cookoo))))

;;> [4 pts] In c%:
(define (size) (add1 (this . doodle . size)))
(define (replace-gaga str)
  (new c% (this . doodle . replace-gaga str)))
(define (same-gaga-cookoo? g c)
  (this . doodle . same-gaga-cookoo? g c))

@@

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
\fi

@@

Unfortunately, code the BU students produced is so convoluted that it
doesn't bear looking at.  All you have to go on is that the \verb|Set|
data structure obeys the following interface:

\begin{verbatim}
;; empty-set is a Set value containing no elements

;; A Set implements:
;; - insert : String -> Set
;;   adds given string to this set, if it isn't already there
;;   (otherwise produces this set)
;; - remove : String -> Set
;;   removes given string from this set, if it's already there
;;   (otherwise produces this set)
;; - size : -> Number
;;   count the elements of this set
;; - has? : String -> Boolean
;;   is the given String in this set?
\end{verbatim}
\noindent
\verb|Set|s should satisfy the following property, called the
``insert-size'' property, for any element and
set:

@@

\begin{solution}
\begin{verbatim}
;; [1 pt -- contract & purpose]
;; pred1 : Set String -> Boolean
;; check the "insert-size" property
;; [4 pts -- code]
(define (pred1 s i)
  (or (and (s . has i) (= (s . insert i . size) (s . size)))
      (and (not (s . has i))
           (= (s . insert i . size) (add1 (s . size))))))

@@

\newpage
Write a new definition of the \verb|fact| method using \verb|Natural|,
and \emph{not} using the built-in numbers of the class system or
DrRacket.  You can assume there is a defined constant \verb|one|,
which is a \verb|Natural| object representing $1$.

>>>>

(define-class a% (fields w))
(define-class b% (fields x y))
(define-class c% (fields z))
\end{verbatim}

@@

\item \verb|replace-x| - produces a \verb|P| like this one, but
  with any \verb|x| field replaced by the given string.

\item \verb|same-x-and-w?| - given two strings, produce true if this
  \verb|P| contains a \verb|B| whose \verb|x| is equal to the
  first given string and whose \verb|y| is an \verb|A| whose
  \verb|w| is equal to the second given string.  Produces false
  otherwise.

@@

\begin{solution}
\begin{verbatim}
;;> [6 pts -- contract and purpose for each method]
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-x : String -> P
;;   Replace x field (if any) of this P with given string.
;; - same-x-and-w? : String String -> Boolean
;;   Is there a B within this P with given x field and w field?

;;> [0 pts -- not required, but write something]
;; An A implements:
;; - w : -> String
;;   Get the w string.

;;> [2 pts] In a%: 
(define (size) 5)
(define (replace-x str) this)
(define (same-x-and-w? g c) false)

;;> [3 pts] In b%:
(define (size) 8)
(define (replace-x str)
  (new b% str (this . y)))
(define (same-x-and-w? g c)
  (and (string=? g (this . x))
       (string=? c (this . y . w))))

;;> [4 pts] In c%:
(define (size) (add1 (this . z . size)))
(define (replace-x str)
  (new c% (this . z . replace-x str)))
(define (same-x-and-w? g c)
  (this . z . same-x-and-w? g c))

@@

@@

Unfortunately, the code the BU students produced is so convoluted that
it doesn't bear looking at.  All you have to go on is that the
\verb|Set| data structure obeys the following interface:

\begin{verbatim}
;; A Set implements:
;; - insert : String -> Set
;;   adds given string to this set, if it isn't already there
;;   (otherwise produces this set)
;; - remove : String -> Set
;;   removes given string from this set, if it's already there
;;   (otherwise produces this set)
;; - size : -> Number
;;   count the elements of this set
;; - has? : String -> Boolean
;;   is the given String in this set?

;; empty-set is a Set value containing no elements
\end{verbatim}
\noindent
\verb|Set|s should satisfy the following property, called the
``insert-size'' property, for any element and
set:

@@

\begin{solution}
\begin{verbatim}
;; [1 pt -- contract & purpose]
;; pred1 : Set String -> Boolean
;; check the "insert-size" property
;; [4 pts -- code]
(define (pred1 s i)
  (= (s . insert i . size)
     (cond [(s . has? i) (add1 (s . size))]
           [else               (s . size)])))

@@

\newpage
Write a new definition of the \verb|fact| method using the
\verb|Natural| interface definition given above, and \emph{not} using
the built-in numbers of the class system or DrRacket.  You can assume
there is a defined constant \verb|one|, which is a \verb|Natural|
object representing $1$.
